Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
typo

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used $5$ and
$10$ as the values of $k$, following the same values as in previous fault
localiztion studies~\cite{ang-perez-van-deursen-rui-2017}.
The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.

>>>>

\subsection{Techniques}
One important independent variable for this study is the scope of
dynamic slicing. Slicing the entire code would be unacceptably
expensive as Critical Slicing needs to re-compile the affected file at
every iteration, \ie{}, after deleting statements and before checking
the oracle (see Section~\ref{sec:slicing}). We control the scope of
slicing through the variable $k$, which denotes the number of distinct
files that dynamic slicing will minimize. In this study, we used $5$ and
$10$ as the values of $k$, following the same values as in previous fault
localization studies~\cite{ang-perez-van-deursen-rui-2017}.
The $k$ files for minimization are selected
from the \sfl{} ranking as follows. First, we build a rank of files by
determining, for each ranked statement, the file that declares
it. Then, we select the top $k$ distinct files from such file ranking.
